Forecasting Gamma-ray Bursts using Gravitational Waves

### 2018-03-10 Paper/Manuscript.tex
Updated paper, Mathematica sections regarding BH-NS

So we will simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
A quick calculation using the above scaling of $\tau_\text{insp}$ shows that even the largest value for $T_\text{AW}$ in Table \ref{table:LIGO2020}
is now less than $ 40\,$ seconds which is too little. Therefore, we simply focus on the capabilities of ET-C.

The LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx}.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.

ISCO location from NR 
\be
\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
\ee

@@

\begin{thebibliography}{}
\bibitem{Regimbau:2012ir}
\bibitem{KAGRA} \url{http://gwcenter.icrr.u-tokyo.ac.jp/en/}
\bibitem{KAGRA2} Akutsu et al. see bibtex
\bibitem{Patricelli:2016bkt}
\bibitem{CE} https://arxiv.org/pdf/1607.08697.pdf
\bibitem{Ozel_Freire} 1603.02698 [astro-ph.HE]
\bibitem{Freire_et_al_2007} The Astrophysical Journal, Volume 675, Issue 1, article id. 670-682, pp. (2008)., arXiv:0711.0925.  
\bibitem{GW170817}
\bibitem{PM1963}
\bibitem{Colpi_Sesana} 1610.05309 [astro-h.HE]
\bibitem{Maggiore}
\bibitem{Blanchet_LRR}
\bibitem{FastestNSspin} J. W. T. Hessels, S. M. Ransom, I. H. Stairs, P. C. C. Freire,
V. M. Kaspi, and F. Camilo, Science 311, 1901 (2006).
\bibitem{SchutzLRR} Schutz, Satyaprakash, LRR
\bibitem{GW170817_Facts} GW170817 Factsheet \url{https://www.ligo.org/detections/GW170817/images-GW170817/GW170817_Factsheet.pdf}.
\bibitem{4PN_EoM_paper} L. Bernard et al., [gr-qc:1711.00283]
\bibitem{Reid} J. Reid, the NS inspiral figure tidal corrections
\bibitem{LIGO_L1_data} Data release for GW170817 \url{https://losc.ligo.org/events/GW170817/}
\bibitem{LIGO_tutorial} LIGO Open Science Center signal processing tutorial at \url{https://losc.ligo.org/s/events/GW150914/GW150914_tutorial.html}
\bibitem{LIGO2020} Advanced LIGO anticipated sensitivity curves at \url{https://dcc.ligo.org/LIGO-T0900288/public}
\bibitem{Hild:2010id} S. Hild et al. Class.Quant.Grav. 28 (2011) 094013  arXiv:1012.0908 [gr-qc]  (see bixtex below)
\bibitem{LSST} LSST
\bibitem{GBM:2017lvd} ApJ paper
\bibitem{Cutler:1994ys}
\bibitem{Farr:2015lna}
\bibitem{Rodriguez:2013oaa}
\bibitem{Read:2009yp}
\bibitem{Andersson:2009yt}
\bibitem{PhysRevD.89.103012}
\bibitem{PhysRevD.91.043002}
\bibitem{Zhu:2017znf}
\bibitem{Cannon:2011vi}
\bibitem{Gabbard:2017lja}
\bibitem{Sathyaprakash:2012jk}
\bibitem{ET_doc}
\bibitem{Sathyaprakash:2012jk}
\bibitem{Wen:2005ui}
\end{thebibliography}

>>>>

So we will simply assume that such lightweight, high-spin BHs exist in BH-NS binaries and compute strains and SNRs accordingly.
A quick calculation shows that these systems yield $T_\text{AW} \lesssim 30\,$seconds in the ALV network of 2020s. %in Table \ref{table:LIGO2020}is now less than $ 40\,$ seconds. 
Therefore, we simply focus on the capabilities of ET which we summarize in Table~\ref{table:ET_BH_NS} below.
%
%
%
\begin{table}[h]
\centering
\begin{tabular}{l|ccccc}
%toprule
\hline
$D\,$(Mpc) & \multicolumn{2}{c}{ET-B} &  & \multicolumn{2}{c}{ET-C}\T\B\\
\hline
{}&  \ \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$ &{}  & \hspace{6mm}$T_\text{AW}$ \hspace{8mm} & $\bar{\rho}_{F}$\T\B\\
%midrule

100 &   28.2 minutes & 503 &{\qquad} &  2.15 hours & 601\T\\
200 & 8.2 minutes & 251  &{\qquad} & 1.1 hours & 300 \\
400 &  2 minutes & 124 &{\qquad} & 34 minutes & 148\\
1000 & 14.3 seconds & 49 &{\qquad} & 14 minutes& 58.5\\
\hline
%bottomrule
\end{tabular}
\caption{Same as Table~\ref{table:ET}, but now for a $5 M_\odot- 1.4 M_\odot$ black hole-neutron star binary.
The SNR is even higher than before, however the advance warning times have decreased significantly.}\label{table:ET_BH_NS}
\end{table}
%
%
\\
\noindent
From the table, we can see that the horizon distance of ET-C for these binaries with $T_\text{AW} \approx 1\,$hour is roughly 200\,Mpc.
Given that the LIGO O1 merger rate for these systems is $ R < 3600\,$Gpc$^{-3}$yr$^{-1}$ \cite{Abbott:2016ymx},
there could be 28.8 such mergers per year within ET-C's horizon distance. We must emphasize that this should be viewed
as an upper limit as low-mass, high-spin black holes such as ours above are expected to be rare.
Therefore, we realistically expect ET-C to forecast $\sim \mathcal{O}(1)$ tidal disruption event per year.
A better estimation would need to incorporate the percentage of such black holes from population studies and Monte-Carlo simulations,
however, all of these come with rather large error bars {\bf CITE}.
%and that no TD occurs for $a=0$. This is roughly consistent with Fig.5 of Ref.~\cite{Hanna:2008um}
%Choosing lower mass implies reduced SNR since $\rho \propto M_c^{5/3} \propto (1+Q)^{1/3}/Q$,
%but even with $m_2=5 M_\odot$, a BH-NS binary is ``louder'' than a BNS system at the same distance. 
%and as we showed in Sec.~\ref{sec:results}, low SNR is not going to be a problem with ET sensitivities out to $D \sim 1\,$Gpc.
%
%It is straightforward to show that this mass bound is only consistent with spinning black holes by substituting the naive Schwarzschild $r_\text{ISCO}$ value 
%into Eq~.(\ref{eq:TD_cond1}) along with $c_R=1.7$ {\bf CITE} which yield $M_\text{BH} \lesssim 4.1 M_\odot$ violating the above BH mass bound.
%ISCO location from NR 
%\be
%\Omega_\text{ISCO} M = 0.068 \left[ 1- \f{0.444}{Q^{1/4}}(1-3.54 C^{1/3})\right] 
%\ee

@@

Table 6
{}&  \ $T_\text{AW}$(sec) \ & $\bar{\rho}_{F}$ &{}  & \ $T_\text{AW}$(sec)\ & $\bar{\rho}_{F}$\T\B\\
%midrule

100 &   1691 & 503 &{\qquad} &  7834 & 601\T\\
200 & 493 & 251  &{\qquad} & 3975 & 300 \\
400 &  118 & 124 &{\qquad} & 2051 & 148\\
1000 & 14.3 & 49 &{\qquad} & 833& 58.5\\
